---
title: "Srtoop deadline: analysis"
author: "Zsuzsa Szekely"
output: 
  html_document: default
editor_options:
  chunk_output_type: console
---
## Load packages

```{r load packages, warning = FALSE, message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, osfr, lme4, BayesFactor, DescTools, sjstats, car, broom, cowplot)
```

## Load helper functions

```{r load helper functions}
source("R/utils.R")
```






# DEADLINE ANALYSIS






# Import data

```{r, message = FALSE, warning = FALSE}
dl_processed_rt <- read_tsv("data/deadline/processed/processed_data_rt.tsv")
dl_processed_acc <- read_tsv("data/deadline/processed/processed_data_acc.tsv")
```

# Descriptive statistics of the sample size
## Number of participants left after exclusion

The number of participants should be the same for the reaction time and the the accuracy as well

```{r, warning = FALSE}
dl_processed_rt %>% 
  distinct(participant_id) %>% 
  count()

dl_processed_acc %>% 
  distinct(participant_id) %>% 
  count()
```

## Number of responses after exclusion
### For the reaction time analysis

```{r, warning = FALSE}
dl_processed_rt %>%
  count()
```

### For the accuracy analysis

```{r, warning = FALSE}
dl_processed_acc %>%
  count()
```

***

# Checking CSE for reaction time
## Figures of CSE for reaction time

```{r, eval= FALSE}
# prepare the cse rt plot
dl_cse_plot_rt_data <-
  dl_processed_rt %>%
  # create congruency text variables
  mutate(isPrevCongruent = case_when(isPrevCongruent ==  0L ~ "Incongruent",
                                     isPrevCongruent ==  1L ~ "Congruent"),
         isCongruent = case_when(congruency ==  "inc" ~ "Incongruent",
                                 congruency ==  "con" ~ "Congruent")) %>%
  # calculate mean rt of each participant
  group_by(participant_id, condition) %>%
  mutate(participant_mean_rt = mean(reaction_time, na.rm = T)) %>%
  # calculate the mean, sd and se of rt incuding all participants' results
  group_by(condition) %>%
  mutate(N = n(),
         mean_rt = mean(participant_mean_rt, na.rm = T),
         sd_rt = sd(participant_mean_rt, na.rm = T),
         se_rt = sd_rt / sqrt(N))

# creating the plot
dl_cse_plot_rt <- dl_cse_plot_rt_data %>% 
  ggplot(aes(x = isPrevCongruent, y = mean_rt,
             color = isCongruent,
             group = isCongruent)) +
  geom_path() +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_rt - se_rt, ymax = mean_rt + se_rt), width=.1) +
  scale_color_manual(values=c("#A8D08C", "#F26C4F")) +
  # scale_y_continuous(limits = c(500, 600)) +
  # scale_x_discrete(expand=c(1, 0)) +
  # ggtitle(stringr::str_to_title()) +
  xlab("Congruency of the previous trial")+
  ylab("Mean reaction time (ms)") +
  guides(color = guide_legend(title="Congruency of \n the current trial")) 
  # + theme(legend.position = c(0.85, 0.5),
  #       axis.line = element_line(color = "black"),
  #       panel.background = element_blank(),
  #       legend.key = element_rect(colour = "transparent", fill = "white"))
```

## Saving the rt CSE figure

```{r, eval= FALSE}
ggsave("figures/deadline/rt_cse.png", width = 14.4, height = 8, plot = last_plot())
```

## Hungarian figures of CSE for reaction time

```{r, eval= FALSE}
# prepare the cse rt plot
dl_cse_plot_rt_data_hun <-
  dl_processed_rt %>%
  # create congruency text variables
  mutate(isPrevCongruent = case_when(isPrevCongruent ==  0L ~ "Inkongruens",
                                     isPrevCongruent ==  1L ~ "Kongruens"),
         isCongruent = case_when(congruency ==  "inc" ~ "Inkongruens",
                                 congruency ==  "con" ~ "Kongruens")) %>%
  # calculate mean rt of each participant
  group_by(participant_id, condition) %>%
  mutate(participant_mean_rt = mean(reaction_time, na.rm = T)) %>%
  # calculate the mean, sd and se of rt incuding all participants' results
  group_by(condition) %>%
  mutate(N = n(),
         mean_rt = mean(participant_mean_rt, na.rm = T),
         sd_rt = sd(participant_mean_rt, na.rm = T),
         se_rt = sd_rt / sqrt(N))

# creating the plot
dl_cse_plot_rt_hun <- dl_cse_plot_rt_data_hun %>% 
  ggplot(aes(x = isPrevCongruent, y = mean_rt,
             color = isCongruent,
             group = isCongruent)) +
  geom_path() +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_rt - se_rt, ymax = mean_rt + se_rt), width=.1) +
  scale_color_manual(values=c("#A8D08C", "#F26C4F")) +
  # scale_y_continuous(limits = c(500, 600)) +
  # scale_x_discrete(expand=c(1, 0)) +
  # ggtitle(stringr::str_to_title()) +
  xlab("Előző próba kongruenciája")+
  ylab("Átlagos reakcióidő (ms)") +
  guides(color = guide_legend(title="Próba \nkongruenciája")) 
  # + theme(legend.position = c(0.85, 0.5),
  #       axis.line = element_line(color = "black"),
  #       panel.background = element_blank(),
  #       legend.key = element_rect(colour = "transparent", fill = "white"))
```

## Saving the rt CSE Hungarian figures

```{r, eval= FALSE}
ggsave("figures/deadline/rt_cse_hun.png", width = 14.4, height = 8, plot = last_plot())
```

# Checking CSE for accuracy in
## Figures of CSE for accuracy

```{r, eval= FALSE}
# prepare the cse rt plot
dl_cse_plot_acc_data <-
  dl_processed_acc %>%
  # create congruency text variables
  mutate(isPrevCongruent = case_when(isPrevCongruent ==  0L ~ "Incongruent",
                                     isPrevCongruent ==  1L ~ "Congruent"),
         isCongruent = case_when(congruency ==  "inc" ~ "Incongruent",
                                 congruency ==  "con" ~ "Congruent")) %>%
  # calculate mean rt of each participant
  group_by(participant_id, condition) %>%
  mutate(participant_mean_acc = mean(correct, na.rm = T)) %>%
  # calculate the mean, sd and se of rt incuding all participants' results
  group_by(condition) %>%
  mutate(N = n(),
         mean_acc = mean(participant_mean_acc, na.rm = T)*100,
         sd_acc = sd(participant_mean_acc, na.rm = T),
         se_acc = sd_acc / sqrt(N))

# creating the plot
dl_cse_plot_acc <- dl_cse_plot_acc_data %>% 
  ggplot(aes(x = isPrevCongruent, y = mean_acc,
             color = isCongruent,
             group = isCongruent)) +
  geom_path() +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_acc - se_acc, ymax = mean_acc + se_acc), width=.1) +
  scale_color_manual(values=c("#A8D08C", "#F26C4F")) +
  # scale_y_continuous(limits = c(500, 600)) +
  # scale_x_discrete(expand=c(1, 0)) +
  # ggtitle(stringr::str_to_title()) +
  xlab("Congruency of the previous trial")+
  ylab("Accuracy (%)") +
  guides(color = guide_legend(title="Congruency of \n the current trial")) 
  # + theme(legend.position = c(0.85, 0.5),
  #       axis.line = element_line(color = "black"),
  #       panel.background = element_blank(),
  #       legend.key = element_rect(colour = "transparent", fill = "white"))
```

## Saving the accuracy CSE figure

```{r, eval= FALSE}
ggsave("figures/deadline/acc_cse.png", width = 14.4, height = 8, plot = last_plot())
```

## Hungarian figures of CSE for accuracy

```{r, eval= FALSE}
# prepare the cse rt plot
dl_cse_plot_acc_data_hun <-
  dl_processed_acc %>%
  # create congruency text variables
  mutate(isPrevCongruent = case_when(isPrevCongruent ==  0L ~ "Inkongruens",
                                     isPrevCongruent ==  1L ~ "Kongruens"),
         isCongruent = case_when(congruency ==  "inc" ~ "Inkongruens",
                                 congruency ==  "con" ~ "Kongruens")) %>%
  # calculate mean rt of each participant
  group_by(participant_id, condition) %>%
  mutate(participant_mean_acc = mean(correct, na.rm = T)) %>%
  # calculate the mean, sd and se of rt incuding all participants' results
  group_by(condition) %>%
  mutate(N = n(),
         mean_acc = mean(participant_mean_acc, na.rm = T)*100,
         sd_acc = sd(participant_mean_acc, na.rm = T),
         se_acc = sd_acc / sqrt(N))

# creating the plot
dl_cse_plot_acc <- dl_cse_plot_acc_data_hun %>% 
  ggplot(aes(x = isPrevCongruent, y = mean_acc,
             color = isCongruent,
             group = isCongruent)) +
  geom_path() +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_acc - se_acc, ymax = mean_acc + se_acc), width=.1) +
  scale_color_manual(values=c("#A8D08C", "#F26C4F")) +
  # scale_y_continuous(limits = c(500, 600)) +
  # scale_x_discrete(expand=c(1, 0)) +
  # ggtitle(stringr::str_to_title()) +
  xlab("Előző próba kongruenciája")+
  ylab("Pontosság (%)") +
  guides(color = guide_legend(title="Próba \nkongruenciája")) 
  # + theme(legend.position = c(0.85, 0.5),
  #       axis.line = element_line(color = "black"),
  #       panel.background = element_blank(),
  #       legend.key = element_rect(colour = "transparent", fill = "white"))
```

## Saving the Hungarian accuracy CSE figure

```{r, eval= FALSE}
ggsave("figures/deadline/acc_cse_hun.png", width = 14.4, height = 8, plot = last_plot())
```








# Reaction time analyis
## I. analysis: Testing whether the CSE was present in the task
### Preprocessing data

We are calculating mean reaction time for the analysis for each participant in each condition.

```{r, warning = FALSE}
dl_processed_rt <- dl_processed_rt %>% 
  group_by(participant_id, condition) %>% 
  mutate(rtConditionalMean = mean(reaction_time, na.rm = TRUE)) %>%
  ungroup()
```

We are calculating the main congruency effect of the current (n) trial, the main congruency effect of the previous trial (n-1) and the interaction effect (CSE) between them for each participant.
```{r}
dl_rt_effect_data <- dl_processed_rt %>% 
  spread(key = condition, value = rtConditionalMean) %>%
  mutate(ii = replace_na(ii, 0),
         ic = replace_na(ic, 0),
         ci = replace_na(ci, 0),
         cc = replace_na(cc, 0)) %>% 
  mutate(congruencyEffect = ((ci + ii) / 2) - ((cc + ic) / 2), # substract the mean rt of congtuent trials from the mean rt of incongtuent trials to get the rt CE
         prevCongruencyEffect = ((ci + cc) / 2) - ((ii + ic) / 2),
         cseEffect = (ci - cc) - (ii - ic))

# check whether there's anybody with more or less than 4 values in for the effects
dl_rt_effect_data %>% 
  group_by(participant_id) %>% 
  distinct(congruencyEffect) %>% 
  count() %>% 
  filter(n != 4) %>% 
  nrow()

dl_rt_effect_data %>% 
  group_by(participant_id) %>% 
  distinct(prevCongruencyEffect) %>% 
  count() %>% 
  filter(n != 4) %>% 
  nrow()

dl_rt_effect_data %>% 
  group_by(participant_id) %>% 
  distinct(cseEffect) %>% 
  count() %>% 
  filter(n != 4) %>% 
  nrow()
```

### Running the analysis

We are running a 2 × 2 repeated-measures ANOVA with mean RT as dependent variable. The two factors of the ANOVA are Previous Trial Congruency (congruent, incongruent) and Current Trial Congruency (congruent, incongruent).

```{r}
dl_rt_anova <- dl_processed_rt %>% 
  aov(rtConditionalMean ~ congruency * isPrevCongruent +
        Error(participant_id / (congruency * isPrevCongruent)), data = .)

# Print results
summary(dl_rt_anova)
```

The interaction was not significant.

We are calculating the partial eta square as an effect size estimate for the ANOVA.

```{r}
dl_rt_anova_eta <- dl_rt_anova %>% 
  effectsize::eta_squared(., partial = TRUE)

# Print results with names
summary(dl_rt_anova_eta)
```




***




# Accuracy analysis
## I. analysis: Testing whether the CSE was present in the different tasks
### Preprocessing data

We are calculating the accuracy for the analysis for each participant in each condition.

```{r calculating mean dev acc}
dl_processed_acc <-
  dl_processed_acc %>% 
  group_by(participant_id, condition) %>% 
  mutate(accConditionalMean = mean(correct, na.rm =)) %>% 
  ungroup()

dl_processed_acc %>% 
  distinct(accConditionalMean) %>% 
  count()
```

We are calculating the main congruency effect of the current (n) trial, the main congruency effect of the previous trial (n-1) and the interaction effect (CSE) between them for each participant.

```{r}
dl_acc_effect_data <- dl_processed_acc %>% 
  spread(key = condition, value = accConditionalMean) %>%
  mutate(ii = replace_na(ii, 0),
         ic = replace_na(ic, 0),
         ci = replace_na(ci, 0),
         cc = replace_na(cc, 0)) %>% 
  mutate(congruencyEffect = ((cc + ic) / 2) - ((ci + ii) / 2), # substract the mean acc of incongruent trials from the mean acc of congruent trials to get the acc CE
         prevCongruencyEffect = ((ci + cc) / 2) - ((ii + ic) / 2),
         cseEffect = (cc - ci) - (ic - ii))

# check whether there's anybody with more or less than 4 values for the effects
dl_acc_effect_data %>% 
  group_by(participant_id) %>% 
  distinct(congruencyEffect) %>% 
  count() %>% 
  filter(n != 4) %>%
  nrow()

dl_acc_effect_data %>% 
  group_by(participant_id) %>% 
  distinct(prevCongruencyEffect) %>% 
  count() %>% 
  filter(n != 4) %>% 
  nrow()

dl_acc_effect_data %>% 
  group_by(participant_id) %>% 
  distinct(cseEffect) %>% 
  count() %>% 
  filter(n != 4) %>%
  nrow()
```

### Running the analysis

We are running a 2 × 2 repeated-measures ANOVA with accuracy as dependent variable. The two factors of the ANOVA are Previous Trial Congruency (congruent, incongruent) and Current Trial Congruency (congruent, incongruent).

```{r}
dl_acc_anova <- dl_processed_acc %>% 
  aov(accConditionalMean ~ congruency * isPrevCongruent +
        Error(participant_id / (congruency * isPrevCongruent)), data = .)

# Print results
summary(dl_acc_anova)
```

All off the effects are significant.

We are calculating the partial eta square as an effect size estimate for the ANOVA.

```{r}
dl_acc_anova_eta <- dl_acc_anova %>% 
  effectsize::eta_squared(., partial = TRUE)

# Print results with names
summary(dl_acc_anova_eta)
```



***



Analysing personal deadline.

Get the mean and sd of deadlines for each participant.
```{r}
personal_deadline <- dl_processed_acc %>% 
  group_by(participant_id) %>% 
  mutate(personal_dl_mean = mean(personalDeadline),
         personal_dl_sd = sd(personalDeadline)) %>%
  distinct(personal_dl_mean)

# plot personal deadlines per each block
personal_deadline_plot <-
  personal_deadline %>%  
  ggplot(aes(personal_dl_mean)) +
  geom_histogram() +
  stat_bin(binwidth = 40) +
  xlab("Personal mean deadline (ms)")

# save plot
ggsave("figures/deadline/personal_deadline.png", width = 14.4, height = 8, plot = last_plot())
```

Examine how personal deadlines change during the task completion (in the 4 different blocks)

```{r}
# plot personal deadlines per each block
block_deadline_plot <-
  dl_processed_acc %>% 
  ggplot(aes(x = blockId, y = personalDeadline)) +
  geom_point() +
  xlab("Block number") +
  ylab("Personal deadline (ms)")

# save plot
ggsave("figures/deadline/deadline_block.png", width = 14.4, height = 8, plot = last_plot())
```








# NODEADLINE ANALYSIS








# Import data

```{r, message = FALSE, warning = FALSE}
nodl_processed_rt <- read_tsv("data/nodeadline/processed/processed_data_rt.tsv")
nodl_processed_acc <- read_tsv("data/nodeadline/processed/processed_data_acc.tsv")
```

# Descriptive statistics of the sample size
## Number of participants left after exclusion

The number of participants should be the same for the reaction time and the the accuracy as well

```{r, warning = FALSE}
nodl_processed_rt %>% 
  distinct(participant_id) %>% 
  count()

nodl_processed_acc %>% 
  distinct(participant_id) %>% 
  count()
```

## Number of responses after exclusion
### For the reaction time analysis

```{r, warning = FALSE}
nodl_processed_rt %>%
  count()
```

### For the accuracy analysis

```{r, warning = FALSE}
nodl_processed_acc %>%
  count()
```

***

# Checking CSE for reaction time
## Figures of CSE for reaction time

```{r, eval= FALSE}
# prepare the cse rt plot
nodl_cse_plot_rt_data <-
  nodl_processed_rt %>%
  # create congruency text variables
  mutate(isPrevCongruent = case_when(isPrevCongruent ==  0L ~ "Incongruent",
                                     isPrevCongruent ==  1L ~ "Congruent"),
         isCongruent = case_when(congruency ==  "inc" ~ "Incongruent",
                                 congruency ==  "con" ~ "Congruent")) %>%
  # calculate mean rt of each participant
  group_by(participant_id, condition) %>%
  mutate(participant_mean_rt = mean(duration, na.rm = T)) %>%
  # calculate the mean, sd and se of rt incuding all participants' results
  group_by(condition) %>%
  mutate(N = n(),
         mean_rt = mean(participant_mean_rt, na.rm = T),
         sd_rt = sd(participant_mean_rt, na.rm = T),
         se_rt = sd_rt / sqrt(N))

# creating the plot
nodl_cse_plot_rt <- nodl_cse_plot_rt_data %>% 
  ggplot(aes(x = isPrevCongruent, y = mean_rt,
             color = isCongruent,
             group = isCongruent)) +
  geom_path() +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_rt - se_rt, ymax = mean_rt + se_rt), width=.1) +
  scale_color_manual(values=c("#A8D08C", "#F26C4F")) +
  # scale_y_continuous(limits = c(500, 600)) +
  # scale_x_discrete(expand=c(1, 0)) +
  # ggtitle(stringr::str_to_title()) +
  xlab("Congruency of the previous trial")+
  ylab("Mean reaction time (ms)") +
  guides(color = guide_legend(title="Congruency of \n the current trial")) 
  # + theme(legend.position = c(0.85, 0.5),
  #       axis.line = element_line(color = "black"),
  #       panel.background = element_blank(),
  #       legend.key = element_rect(colour = "transparent", fill = "white"))
```

## Saving the rt CSE figure

```{r, eval= FALSE}
ggsave("figures/nodeadline/rt_cse.png", width = 14.4, height = 8, plot = last_plot())
```

## Hungarian figures of CSE for reaction time

```{r, eval= FALSE}
# prepare the cse rt plot
nodl_cse_plot_rt_data_hun <-
  nodl_processed_rt %>%
  # create congruency text variables
  mutate(isPrevCongruent = case_when(isPrevCongruent ==  0L ~ "Inkongruens",
                                     isPrevCongruent ==  1L ~ "Kongruens"),
         isCongruent = case_when(congruency ==  "inc" ~ "Inkongruens",
                                 congruency ==  "con" ~ "Kongruens")) %>%
  # calculate mean rt of each participant
  group_by(participant_id, condition) %>%
  mutate(participant_mean_rt = mean(duration, na.rm = T)) %>%
  # calculate the mean, sd and se of rt incuding all participants' results
  group_by(condition) %>%
  mutate(N = n(),
         mean_rt = mean(participant_mean_rt, na.rm = T),
         sd_rt = sd(participant_mean_rt, na.rm = T),
         se_rt = sd_rt / sqrt(N))

# creating the plot
nodl_cse_plot_rt_hun <- nodl_cse_plot_rt_data_hun %>% 
  ggplot(aes(x = isPrevCongruent, y = mean_rt,
             color = isCongruent,
             group = isCongruent)) +
  geom_path() +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_rt - se_rt, ymax = mean_rt + se_rt), width=.1) +
  scale_color_manual(values=c("#A8D08C", "#F26C4F")) +
  # scale_y_continuous(limits = c(500, 600)) +
  # scale_x_discrete(expand=c(1, 0)) +
  # ggtitle(stringr::str_to_title()) +
  xlab("Előző próba kongruenciája")+
  ylab("Átlagos reakcióidő (ms)") +
  guides(color = guide_legend(title="Próba \nkongruenciája")) 
  # + theme(legend.position = c(0.85, 0.5),
  #       axis.line = element_line(color = "black"),
  #       panel.background = element_blank(),
  #       legend.key = element_rect(colour = "transparent", fill = "white"))
```

## Saving the rt CSE Hungarian figures

```{r, eval= FALSE}
ggsave("figures/nodeadline/rt_cse_hun.png", width = 14.4, height = 8, plot = last_plot())
```

# Checking CSE for accuracy in
## Figures of CSE for accuracy

```{r, eval= FALSE}
# prepare the cse rt plot
nodl_cse_plot_acc_data <-
  nodl_processed_acc %>%
  # create congruency text variables
  mutate(isPrevCongruent = case_when(isPrevCongruent ==  0L ~ "Incongruent",
                                     isPrevCongruent ==  1L ~ "Congruent"),
         isCongruent = case_when(congruency ==  "inc" ~ "Incongruent",
                                 congruency ==  "con" ~ "Congruent")) %>%
  # calculate mean rt of each participant
  group_by(participant_id, condition) %>%
  mutate(participant_mean_acc = mean(correct, na.rm = T)) %>%
  # calculate the mean, sd and se of rt incuding all participants' results
  group_by(condition) %>%
  mutate(N = n(),
         mean_acc = mean(participant_mean_acc, na.rm = T)*100,
         sd_acc = sd(participant_mean_acc, na.rm = T),
         se_acc = sd_acc / sqrt(N))

# creating the plot
nodl_cse_plot_acc <- nodl_cse_plot_acc_data %>% 
  ggplot(aes(x = isPrevCongruent, y = mean_acc,
             color = isCongruent,
             group = isCongruent)) +
  geom_path() +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_acc - se_acc, ymax = mean_acc + se_acc), width=.1) +
  scale_color_manual(values=c("#A8D08C", "#F26C4F")) +
  # scale_y_continuous(limits = c(500, 600)) +
  # scale_x_discrete(expand=c(1, 0)) +
  # ggtitle(stringr::str_to_title()) +
  xlab("Congruency of the previous trial")+
  ylab("Accuracy (%)") +
  guides(color = guide_legend(title="Congruency of \n the current trial")) 
  # + theme(legend.position = c(0.85, 0.5),
  #       axis.line = element_line(color = "black"),
  #       panel.background = element_blank(),
  #       legend.key = element_rect(colour = "transparent", fill = "white"))
```

## Saving the accuracy CSE figure

```{r, eval= FALSE}
ggsave("figures/nodeadline/acc_cse.png", width = 14.4, height = 8, plot = last_plot())
```

## Hungarian figures of CSE for accuracy

```{r, eval= FALSE}
# prepare the cse rt plot
nodl_cse_plot_acc_data_hun <-
  nodl_processed_acc %>%
  # create congruency text variables
  mutate(isPrevCongruent = case_when(isPrevCongruent ==  0L ~ "Inkongruens",
                                     isPrevCongruent ==  1L ~ "Kongruens"),
         isCongruent = case_when(congruency ==  "inc" ~ "Inkongruens",
                                 congruency ==  "con" ~ "Kongruens")) %>%
  # calculate mean rt of each participant
  group_by(participant_id, condition) %>%
  mutate(participant_mean_acc = mean(correct, na.rm = T)) %>%
  # calculate the mean, sd and se of rt incuding all participants' results
  group_by(condition) %>%
  mutate(N = n(),
         mean_acc = mean(participant_mean_acc, na.rm = T)*100,
         sd_acc = sd(participant_mean_acc, na.rm = T),
         se_acc = sd_acc / sqrt(N))

# creating the plot
nodl_cse_plot_acc <- nodl_cse_plot_acc_data_hun %>% 
  ggplot(aes(x = isPrevCongruent, y = mean_acc,
             color = isCongruent,
             group = isCongruent)) +
  geom_path() +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_acc - se_acc, ymax = mean_acc + se_acc), width=.1) +
  scale_color_manual(values=c("#A8D08C", "#F26C4F")) +
  # scale_y_continuous(limits = c(500, 600)) +
  # scale_x_discrete(expand=c(1, 0)) +
  # ggtitle(stringr::str_to_title()) +
  xlab("Előző próba kongruenciája")+
  ylab("Pontosság (%)") +
  guides(color = guide_legend(title="Próba \nkongruenciája")) 
  # + theme(legend.position = c(0.85, 0.5),
  #       axis.line = element_line(color = "black"),
  #       panel.background = element_blank(),
  #       legend.key = element_rect(colour = "transparent", fill = "white"))
```

## Saving the Hungarian accuracy CSE figure

```{r, eval= FALSE}
ggsave("figures/nodeadline/acc_cse_hun.png", width = 14.4, height = 8, plot = last_plot())
```








# Reaction time analyis
## I. analysis: Testing whether the CSE was present in the task
### Preprocessing data

We are calculating mean reaction time for the analysis for each participant in each condition.

```{r, warning = FALSE}
nodl_processed_rt <- nodl_processed_rt %>% 
  group_by(participant_id, condition) %>% 
  mutate(rtConditionalMean = mean(duration, na.rm = TRUE)) %>%
  ungroup()
```

We are calculating the main congruency effect of the current (n) trial, the main congruency effect of the previous trial (n-1) and the interaction effect (CSE) between them for each participant.
```{r}
nodl_rt_effect_data <- nodl_processed_rt %>% 
  spread(key = condition, value = rtConditionalMean) %>%
  mutate(ii = replace_na(ii, 0),
         ic = replace_na(ic, 0),
         ci = replace_na(ci, 0),
         cc = replace_na(cc, 0)) %>% 
  mutate(congruencyEffect = ((ci + ii) / 2) - ((cc + ic) / 2), # substract the mean rt of congtuent trials from the mean rt of incongtuent trials to get the rt CE
         prevCongruencyEffect = ((ci + cc) / 2) - ((ii + ic) / 2),
         cseEffect = (ci - cc) - (ii - ic))

# check whether there's anybody with more or less than 4 values in for the effects
nodl_rt_effect_data %>% 
  group_by(participant_id) %>% 
  distinct(congruencyEffect) %>% 
  count() %>% 
  filter(n != 4) %>% 
  nrow()

nodl_rt_effect_data %>% 
  group_by(participant_id) %>% 
  distinct(prevCongruencyEffect) %>% 
  count() %>% 
  filter(n != 4) %>% 
  nrow()

nodl_rt_effect_data %>% 
  group_by(participant_id) %>% 
  distinct(cseEffect) %>% 
  count() %>% 
  filter(n != 4) %>% 
  nrow()
```

### Running the analysis

We are running a 2 × 2 repeated-measures ANOVA with mean RT as dependent variable. The two factors of the ANOVA are Previous Trial Congruency (congruent, incongruent) and Current Trial Congruency (congruent, incongruent).

```{r}
nodl_rt_anova <- nodl_processed_rt %>% 
  aov(rtConditionalMean ~ congruency * isPrevCongruent +
        Error(participant_id / (congruency * isPrevCongruent)), data = .)

# Print results
summary(nodl_rt_anova)
```

The interaction was not significant.

We are calculating the partial eta square as an effect size estimate for the ANOVA.

```{r}
nodl_rt_anova_eta <- nodl_rt_anova %>% 
  effectsize::eta_squared(., partial = TRUE)

# Print results with names
summary(nodl_rt_anova_eta)
```




***




# Accuracy analysis
## I. analysis: Testing whether the CSE was present in the different tasks
### Preprocessing data

We are calculating the accuracy for the analysis for each participant in each condition.

```{r calculating mean dev acc}
nodl_processed_acc <-
  nodl_processed_acc %>% 
  group_by(participant_id, condition) %>% 
  mutate(accConditionalMean = mean(correct, na.rm =)) %>% 
  ungroup()

nodl_processed_acc %>% 
  distinct(accConditionalMean) %>% 
  count()
```

We are calculating the main congruency effect of the current (n) trial, the main congruency effect of the previous trial (n-1) and the interaction effect (CSE) between them for each participant.

```{r}
nodl_acc_effect_data <- nodl_processed_acc %>% 
  spread(key = condition, value = accConditionalMean) %>%
  mutate(ii = replace_na(ii, 0),
         ic = replace_na(ic, 0),
         ci = replace_na(ci, 0),
         cc = replace_na(cc, 0)) %>% 
  mutate(congruencyEffect = ((cc + ic) / 2) - ((ci + ii) / 2), # substract the mean acc of incongruent trials from the mean acc of congruent trials to get the acc CE
         prevCongruencyEffect = ((ci + cc) / 2) - ((ii + ic) / 2),
         cseEffect = (cc - ci) - (ic - ii))

# check whether there's anybody with more or less than 4 values for the effects
nodl_acc_effect_data %>% 
  group_by(participant_id) %>% 
  distinct(congruencyEffect) %>% 
  count() %>% 
  filter(n != 4) %>%
  nrow()

nodl_acc_effect_data %>% 
  group_by(participant_id) %>% 
  distinct(prevCongruencyEffect) %>% 
  count() %>% 
  filter(n != 4) %>% 
  nrow()

nodl_acc_effect_data %>% 
  group_by(participant_id) %>% 
  distinct(cseEffect) %>% 
  count() %>% 
  filter(n != 4) %>%
  nrow()
```

### Running the analysis

We are running a 2 × 2 repeated-measures ANOVA with accuracy as dependent variable. The two factors of the ANOVA are Previous Trial Congruency (congruent, incongruent) and Current Trial Congruency (congruent, incongruent).

```{r}
nodl_acc_anova <- nodl_processed_acc %>% 
  aov(accConditionalMean ~ congruency * isPrevCongruent +
        Error(participant_id / (congruency * isPrevCongruent)), data = .)

# Print results
summary(nodl_acc_anova)
```

All off the effects are significant.

We are calculating the partial eta square as an effect size estimate for the ANOVA.

```{r}
nodl_acc_anova_eta <- nodl_acc_anova %>% 
  effectsize::eta_squared(., partial = TRUE)

# Print results with names
summary(nodl_acc_anova_eta)
```








# COMPARING DEADLINE AND NO-DEADLINE DATA
We would like to know if there is significant difference 
* 1. between the CSE scores of dl and no-dl data.
* 2. in the variance of accuracy between the dl and no-dl condition.

## Comparing CSE scores

As we only had significant CSE in case of accuracy (both in the experimental and the control group), we analyze only these data.

Create df containing dl and nodl CSE data as well.
```{r}
cse_acc_control <- dl_acc_effect_data %>%
  mutate(group = "control")

cse_acc_exp <- nodl_acc_effect_data %>% 
  mutate(group = "experimetnal")

cse_acc_all <-
  bind_rows(cse_acc_control, cse_acc_exp)
```

Check if the distributions of the data are appropriate for an independent t-test.
```{r}

```

